Postural developments modulate children's visual access to social information

### 2020-04-29 writeup-paper/draft_apa_march2020.tex
clean up writing repository

\documentclass[english,man,floatsintext,draftall]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdftitle={Postural developments modulate children's visual access to social information},
            pdfkeywords={Postural developments modulate children's visual access to social
information},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=english]{babel}
\else
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\fi
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

Correspondence concerning this article should be addressed to Bria L. Long, 450 Serra Mall, Stanford CA 94305. E-mail: bria@stanford.edu}
\keywords{Postural developments modulate children's visual access to social information\newline\indent Word count: X}
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}

@@

\abstract{
The ability to process social information is a critical component of
children's early language and cognitive development. However, as
children reach their first birthday, they begin to locomote themselves,
dramatically affecting their visual access to this information. How do
these postural and locomotor changes affect children's access to the
social information relevant for word-learning? Here, we explore this
question by using head-mounted cameras to record 36 infants' (8-16
months of age) egocentric visual perspective and use computer vision
algorithms to estimate the proportion of faces and hands in infants'
environments. We find that infants' posture and orientation to their
caregiver modulates their access to social information, confirming
previous work that suggests motoric developments play a significant role
in the emergence of children's linguistic and social capacities. In
addition, we applied our automated analysis to the headcam data from a
recent paper showing similar effects postre on visual attention
(Franchak et al., 2017), finding convergence across methodologies,
laboratories, and datasets. We suggest that the combined use of
head-mounted cameras and the application of new computer vision
techniques is a promising avenue for understanding the statistics of
infants' visual and linguistic experience as they change over
development.
}

@@

From their earliest months, infants are deeply engaged in learning from
others. Even newborns tend to prefer to look at faces with direct
vs.~averted gaze (Farroni, Csibra, Simion, \& Johnson, 2002) and young
infants follow overt gaze shifts. And as infants learn to parse and
segment their native language(s), the social cues provided by speakers
(e.g., eye-gaze) may provide strong scaffolding for early word learning.
Indeed, empirical work suggests that children's ability to process
social cues is a key factor in early language development: in a
longitudinal study, children's level of joint engagement with their
mother at 9-12 months was found to predict both their receptive and
productive vocabularies (Carpenter, Nagell, \& Tomasello, 1998). More
specifically, 10 month-olds who follow an adult's gaze in an
experimental context have larger vocabularies at 18 months and
throughout the second year of life (R. Brooks \& Meltzoff, 2005; Rechele
Brooks \& Meltzoff, 2008).

Around their first birthday, however, children's ability to interact
with their world radically changes (Adolph \& Berger, 2006) as they are
no longer constrained to the same spot that their caregivers last placed
them in. Before the first birthday, children often begin crawling; soon
after, they begin to walk independently. While not all children crawl
({\textbf{???}})---or crawl in the same way---children tend to find
creative ways of moving (e.g., scooting) or getting others to help them
move (e.g cruising) to begin to explore their world on their own
({\textbf{???}}). And as independent agents in the world, children are
more active in the construction of their own learning environments. Yet
while toddlers do determine their own input to a much greater degree,
they spend much of their time in a world primarily populated by knees

One possibility is that these motor improvements have strong
developmental cascades, impacting children's emerging social, cognitive,
and linguistic abilities (Iverson, 2010). Indeed, these postural changes
change how children interact with their mothers; walking infants make
different kinds of object-related bids for attention from their mothers
than crawling infants, and tend to hear more action directed statements
(e.g., \enquote{open it}) (Karasik, Tamis-LeMonda, \& Adolph, 2014). In
an observational study, Walle and Campos (2014) also found that children
who were able to walk had both higher receptive and productive
vocabularies. On their account, children's ability to stand and
independently locomote may fundamentally change their ability to access
the social information (e.g., faces, gaze) relative to children who are
still crawling and sitting. In other words, the ability of walking
infants to access more detailed social information may allow infants to
learn words quicker and more efficiently, facilitating language growth.

Over the past decade, researchers have started to use egocentric,
head-mounted cameras to document the social information that infants and
children have access to across early development, and to understand the
degree to which there are substantial shifts in their viewpoints that
may have downstream developmental consequences ({\textbf{???}}). Indeed,
the infant visual perspective has proved to be both remarkably different
than the adult perspective and not easily predicted by our own
intuitions (Clerkin, Hart, Rehg, Yu, \& Smith, 2017; Franchak, Kretch,
Soska, \& Adolph, 2011, Yoshida and Smith (2008)). Over the first two
years of life, the infant viewpoint transitions from primarily
containing close up view of faces to capturing relatively restricted
views of hands paired with the objects they are acting on (Fausey,
Jayaraman, \& Smith, 2016); both computational and empirical work
suggest that this restricted viewpoint is more effective for learning
about objects and their labels than the comparable adult perspective (D.
Yurovsky, Smith, \& Yu, in press, Bambach, Crandall, Smith, and Yu
(2017)).

Here, we directly examine the role that postural developments that
infants' experience as they reach their first birthday change the social
information in the infant view. We hypothesize that children's postural
developments may be partially responsible for some of these changes in
the infant perspective. During spontaneous play, toddlers are more
likely to look at the floor while crawling than while walking (Franchak
et al., 2011), when they have full visual access to their environment
and the people in it (Kretch, Franchak, and Adolph, 2014). More
recently, when 12-month-olds ({\textbf{???}}) participated in a
free-play session with their caregivers, their own posture and as well
as their caregiver's posture influenced the proportion of time they
spent looking at the faces and bodies of their caregivers
({\textbf{???}}).

Here, we expand on these previous findings in three key ways. First,
using head-mounted cameras during a brief laboratory free-play session,
we record the visual experience of three groups of children at 8, 12,
and 16 months-of-age, covering a broad range of ages and locomotor
abilities around the first birthday; Children's posture and orientation
relative to their caregiver were also recorded from a third-person
perspective and hand-annotated. This cross-sectional design thus allows
us to directly examine the relative contributions of age vs.~postural
developments on children's visual access to social information. Second,
we use a modern computer vision algorithm for the automated detection of
faces and hands in the egocentric viewpoints of infants. In particular,
we capitalize on recent improvements in face and pose detection
algorithms (Cao, Simon, Wei, \& Sheikh, 2017; K. Zhang, Zhang, Li, \&
Qiao, 2016) to analyze the frequencies of faces and hands in the child's
visual environment, both overall and relative to naming events by their
caregivers. Use of this emerging technology allows us to annotate the
entirety of the dataset, allowing a more complete picture of the
changing infant perspective. In addition, we extend this technique to
the same dataset used in ({\textbf{???}}), replicating their main
pattern of results using this novel methodology and finding convergence
between our datasets with different play sessions, populations, and
head-mounted cameras. Finally, as parents were presented with pairs of
novel and familiar objects with their children during the play sessions,
we directly examine the availability of social signals during naming
events.

Thus, our current dataset allows us to analyze changes in the visual
access to faces and hands according to children's age, posture, and
linguistic input. We predicted that there would be differential access
to social information based on children's postural developments:
crawling infants would see fewer faces/hands because they would
primarily be looking at the ground, while walking toddlers would have
access to a richer visual landscape with greater access to the social
information in their environment. {[}language predictions?{]}

@@

To obtain this final sample, we tested 95 children, excluding 59
children for the following reasons: 20 for technical issues related to
the headcam, 15 for failing to wear the headcam, 10 for fewer than 4
minutes of headcam footage, 5 for having multiple adults present, 5 for
missing Communicative Development Inventory (CDI) data, 2 for missing
scene camera footage, 1 for fussiness, and one for sample symmetry. All
inclusion decisions were made independent of the results of subsequent
analyses. Some of these data were also analyzed in Frank, Simmons,
Yurovsky, and Pusiol (2013).

@@

The first face detection system made use of a series of Haar
feature-based cascade classifiers (Viola \& Jones, 2004) applied to each
individual frame. The second algorithm (based on work by K. Zhang et al.
(2016)) uses multi-task cascaded convolutional neural networks (MTCNNs)
for joint face detection and alignment, built to perform well in
real-world environments where varying illuminations and occlusions are
present. We used a Tensorflow implementation of this algorithm avaliable
at \url{https://github.com/davidsandberg/facenet}.

@@

For face detection, MTCNN outperformed OpenPose when taking into account
only the composite F-score (0.89 MTCNN vs.~0.83 OpenPose). Although
MTCNN and OpenPose performed comparably with the random sample, MTCNN
performed better on the high density sample (specifically looking at
precision), suggesting that OpenPose generated more false positives than
MTCNN. ViolaJones performed quite poorly relative to the other
detectors, especially with respect to the random sample. We thus use
MTCNN detections in the following analyses. For wrist detection,
OpenPose performed moderately well (F = 0.74) with relatively high
precision but low recall on the randomly sampled frames (see Table 1).
We thus analyze wrist detections, with the caveat that we are likely
underestimating the proportion of hands in the dataset.

\begin{table}[ht]
\centering
\begin{tabular}{rllrrr}
\hline
Algorithm & Sample\ Type & P & R & F \\ 
\hline
MTCNN-Faces & High density & 0.89 & 0.92 & \textbf{0.90} \\ 
MTCNN-Faces & Random & 0.94 & 0.62 & 0.75 \\ 
OpenPose-Faces & High density & 0.78 & 0.93 & 0.84 \\ 
OpenPose-Faces & Random & 0.72 & 0.80 & \textbf{0.76} \\ 
ViolaJones-Faces & High density & 0.96 & 0.44 & 0.60 \\ 
ViolaJones-Faces & Random & 0.44 & 0.38 & 0.41 \\ 
OpenPose-Wrists & High density & 0.66 & 1.00 & 0.79 \\ 
OpenPose-Wrists & Random & 0.88 & 0.29 & 0.44 \\ 
\hline
\end{tabular}
\caption{Detector performance on both high density samples (where proportion of targets detected was high) and random samples (where frames were randomly selected). P, R, and F denote precision, recall, and F-score, respectively. Scores in bold are the highest F-scores for each sample type.} 
\vspace{-1em}
\end{table}

@@

First, we report developmental shifts in infants' posture and their
orientation relative to their caregiver, consistent with previous
literature ({\textbf{???}}, {\textbf{???}}). Then, we examine how these
changes influence children's visual access to faces and wrists/hands
across this developmental time range, examining the relative
contributions of age vs.~postural developments. We also explore how
these changes impact the accessibility of faces and wrists/hands during
labeling events, both when parents were labeling familiar objects (e.g.,
\enquote{cat}) as well as novel objects (e.g., \enquote{zem}). Finally,
we apply the same automated detection method to a egocentric video
dataset collected by a different lab ({\textbf{???}}) during which
children's in-the-moment posture was annotated, replicating their
existing results and finding converging support across methods, labs,
and paradigms for the impact of postural developments on children's
visual access to social information.

\begin{figure*}[h]

{\centering \includegraphics{figs/posture-1}

@@

\begin{figure*}[h]

{\centering \includegraphics{figs/indivPosOrient-1}

@@

We first examined the proportion of face and hand detections as a
function of children's age without considering their posture (see Figure
\ref{fig:detByAge}). While faces tended to be in the field-of-view
overall more often than hands, children's head-mounted cameras were
angled slightly upward to capture the presence of faces, and hand
detections suffered from somewhat lower recall than face detections.
Going forward, we thus analyze differences in the relative proportion of
faces or hands in view as a function of age, posture, and orientation,
rather than comparing them directly. Overall, we observed that
12-month-olds appeared to have visual access to slightly fewer faces
than 8 or 16-month-olds, creating a slight U-shaped function in face
detections; conversely, hand detections were showed a slight increase
across this age range, as reported in prior literature ({\textbf{???}}).

However, these age-related trends were much smaller than the effect of
infant's postural developments on children's visual access to faces and
hands. Children's in-the-moment posture was a major factor both in how
many faces and hands were in view during the play session, as was their
orientation relative to their caregiver. Infants who were sitting or
standing had more faces in view than infants who were lying
down/crawling (i.e.~prone), which was most frequent among 12-month-olds
relative to the other age groups (Figure \ref{fig:detByPosOrient}). When
caregivers were behind their children, supporting their children's
sitting or standing positions, children saw fewer faces and wrists. In
particular, children who were sitting or in front of their caregiver had
a high proportion of faces and hands in their field of view. (Figure
\ref{fig:detByPosOrient}, lower panel).

@@

Our play session was designed to provide parents with opporunities to
label objects--both familiar and novel--such that we could examine
whether children seek out different kinds of social information around
naming events. We thus explored how face and hand detections changed
during object labeling events, analyzing a four-second window around
each labeling event (e.g., \enquote{Look at the {[}zem{]}!}). Every
utterance of one of the labelled objects (e.g., \enquote{ball}) was
counted as a \enquote{labeling event}; timestamps of the beginning of
each word were hand-annotated from transcripts ad synchronized with the
frame-by-frame detections. Overall, we did not find major differences in
face/hand detections during naming events relative to baseline, either
for novel objects or for familiar objects (see Figure
\ref{fig:detByNaming}). This was true both when we analyzed naming rates
with or without taking into account children's posture and orientation
relative to their caregiver. These results suggest that either children
did not actively seek out social information during this particular play
session around naming events, perhaps because were a limited number of
possible referents at any given time.

\begin{figure*}[h]

{\centering \includegraphics{figs/detByAge-1}

@@

\begin{figure*}[h]

{\centering \includegraphics{figs/detByPosOrient-1}

@@

\begin{figure*}[h]

{\centering \includegraphics{figs/detByNaming-1}

@@

\section{Extension to Franchak et al.,
2017}\label{extension-to-franchak-et-al.-2017}

In the present work, we found that infant's in-the-moment posture
changed with their age, as did infants' orientation relative their
caregiver. In a related study with 12-month-olds, ({\textbf{???}}) also
that children's in-the-moment posture changed the amount of time infants
spent looking at faces. Here, we sought to replicate the findings from
({\textbf{???}}) using our automated methodology (OpenPose detections),
using the footage from their head-mounted cameras (shared on Databrary,
({\textbf{???}})).

This dataset differed from the present in two key ways that could
present a challenge for our automated methodology. First, the
environment that infants were immersed in with their caregivers (and
experimenters) was much larger and more varied than the play room used
in the present dataset, containing multiple structures and toys in
different parts of the room for infants to explore, unlike the present
room dataset which was relatively small (approximately 10' x 10'). Thus,
our automated methodology could fail to generalize to scenes from these
more complex environments, where detecting faces and hands could
arguably be a much harder task. Second, ({\textbf{???}}) used a
head-mounted eye-tracker, finding that children's posture affected where
children were looking within their visual field. Nonetheless, if
children are often orienting their heads towards where they are
allocating their attention ({\textbf{???}}) then we should expect to
find the same pattern of results only when analyzing the information in
view.

\begin{figure*}[h]

{\centering \includegraphics{figs/franchak-1}

>>>>

\documentclass[english,man,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdftitle={Postural developments modulate children's visual access to social information},
            pdfkeywords={Postural developments modulate children's visual access to social
information},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=english]{babel}
\else
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\fi
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

Correspondence concerning this article should be addressed to Bria L. Long, 450 Serra Mall, Stanford CA 94305. E-mail: bria@stanford.edu}
\keywords{Postural developments modulate children's visual access to social information\newline\indent Word count: X}
\usepackage{csquotes}

@@

\abstract{
The ability to process social information is a critical component of
children's early linguistic and cognitive development. However, as
children reach their first birthday, they begin to locomote themselves,
dramatically changing the way they see the world around them. How do
these postural and locomotor developments affect children's access to
the social information relevant for word-learning? We explored this
question by using head-mounted cameras to record the egocentric visual
perspective of 36 infants' (at 8, 12, and 16 months of age) during a
naturalistic play session with their caregiver. To estimate the
proportion of faces and hands in the infant view, we used a computer
vision algorithm to detect the presence of faces and hands in the entire
dataset. We found that infants' posture and orientation to their
caregiver changed dramatically across this age range and modulated their
access to this social information; infants who were sitting or standing
with their caregiver at a close distance tended to have the most
faces/hands in their visual field. We also applied our automated
analysis to the egocentric video data from a recent paper documenting
how posture changes one-year-olds visual access to faces (Franchak et
al., 2017), finding convergence across both methodologies and dataset
and confirming previous work that motoric developments play a
significant role in the emergence of children's linguistic and social
capacities. We suggest that the combined use of head-mounted cameras and
the application of new computer vision techniques is a promising avenue
for understanding the statistics of infants' visual and linguistic
experience as they change over development.
}

@@

From their earliest months, infants are deeply engaged in learning from
others. Even newborns tend to prefer to look at faces with direct
vs.~averted gaze (Farroni, Csibra, Simion, \& Johnson, 2002) and young
infants follow overt gaze shifts. And as infants learn to parse and
segment their native language(s), the social cues provided by speakers
(e.g., eye-gaze) may provide strong scaffolding for early word learning.
Indeed, empirical work suggests that children's ability to process
social cues is a key factor in early language development: in a
longitudinal study, children's level of joint engagement with their
mother at 9-12 months was found to predict both their receptive and
productive vocabularies (Carpenter, Nagell, \& Tomasello, 1998). More
specifically, 10 month-olds who follow an adult's gaze in an
experimental context have larger vocabularies at 18 months and
throughout the second year of life (Brooks \& Meltzoff, 2005, 2008).

Around their first birthday, however, children's ability to interact
with their world radically changes (Adolph \& Berger, 2006) as they are
no longer constrained to the same spot that their caregivers last placed
them in. Before the first birthday, children often begin crawling; soon
after, they begin to walk independently. While not all children crawl
(Adolph, Vereijken, \& Denny, 1998)---or crawl in the same
way---children tend to find creative ways of moving (e.g., scooting) or
getting others to help them move (e.g cruising) to begin to explore
their world on their own (Patrick, Noah, \& Yang, 2012). As independent
agents in the world, children are more active in the construction of
their own learning environments--yet spend much of their time in a world
primarily populated by knees

One possibility is that these motor improvements have strong
developmental cascades, impacting children's emerging social, cognitive,
and linguistic abilities (Iverson, 2010). Indeed, these postural changes
change how children interact with their mothers; walking infants make
different kinds of object-related bids for attention from their mothers
than crawling infants, and tend to hear more action directed statements
(e.g., \enquote{open it}) (Karasik, Tamis-LeMonda, \& Adolph, 2014). In
an observational study, Walle and Campos (2014) also found that children
who were able to walk had both higher receptive and productive
vocabularies. On their account, children's ability to stand and
independently locomote may fundamentally change their ability to access
the social information (e.g., facial expressions, gaze cues, pointing)
relative to children who are still crawling and sitting. In other words,
the ability of walking infants to access more detailed social
information may allow infants to learn words quicker and more
efficiently, facilitating language growth.

Over the past decade, researchers have started to use egocentric,
head-mounted cameras to document the social information that infants and
children have access to across early development, and to understand the
degree to which there are substantial shifts in their viewpoints that
may have downstream developmental consequences (Yoshida \& Smith, 2008).
Indeed, the infant visual perspective has proved to be both remarkably
different than the adult perspective and not easily predicted by our own
intuitions (Franchak, Kretch, Soska, \& Adolph, 2011, Yoshida and Smith
(2008), Clerkin, Hart, Rehg, Yu, and Smith (2017)). Over the first two
years of life, the infant viewpoint seems to transition from primarily
containing close up view of faces to capturing relatively restricted
views of hands paired with the objects they are acting on (Fausey,
Jayaraman, \& Smith, 2016); both computational and empirical work
suggest that this restricted viewpoint may be more effective for
learning about objects and their labels than the comparable adult
perspective (D. Yurovsky, Smith, \& Yu, 2012, Bambach, Crandall, Smith,
and Yu (2017)).

We hypothesized that children's postural developments may be partially
responsible for some of these changes in the infant perspective. During
spontaneous play, toddlers are more likely to look at the floor while
crawling than while walking (Franchak et al., 2011), when they have full
visual access to their environment and the people in it (Kretch,
Franchak, and Adolph, 2014). More recently, when 12-month-olds
(Franchak, Kretch, \& Adolph, 2017) participated in a free-play session
with their caregivers, their own posture and as well as their
caregiver's posture influenced the proportion of time they spent looking
at the faces and bodies of their caregivers (Franchak et al., 2017).

Here, we directly examine the role that postural developments that
infants' experience as they reach their first birthday change the social
information in the infant view. We expand on previous findings in three
key ways. First, using head-mounted cameras during a brief laboratory
free-play session, we record the visual experience of three groups of
children at 8, 12, and 16 months-of-age, covering a broad range of ages
and locomotor abilities around the first birthday; Children's posture
and orientation relative to their caregiver were also recorded from a
third-person perspective and hand-annotated. This cross-sectional design
thus allows us to directly examine the relative contributions of age
vs.~postural developments on children's visual access to social
information. Second, we use a modern computer vision algorithm for the
automated detection of faces and hands in the egocentric viewpoints of
infants. In particular, we capitalize on recent improvements in face and
pose detection algorithms (Cao, Simon, Wei, \& Sheikh, 2017; K. Zhang,
Zhang, Li, \& Qiao, 2016) to analyze the frequencies of faces and hands
in the child's visual environment, both overall and relative to naming
events by their caregivers. Use of this emerging technology allows us to
annotate the entirety of the dataset, allowing a more complete picture
of the changing infant perspective. We apply this same automated method
to the dataset used in Franchak et al. (2017), validating the
generalizability of this technique. Third, as parents were presented
with pairs of novel and familiar objects with their children during the
play sessions, we were able to explore the availability of social
signals during naming events.

Thus, the current study allows us to analyze changes in the visual
access to faces and hands according to children's age, posture, and
linguistic input. Broadly, we predicted that there would be differential
access to social information based on children's postural developments:
crawling infants would see fewer faces/hands because they would
primarily be looking at the ground, while walking toddlers would have
access to a richer visual landscape with greater access to the social
information in their environment.

@@

To obtain this final sample, we tested 95 children, excluding 59
children for the following reasons: 20 for technical issues related to
the headcam, 15 for failing to wear the headcam, 10 for fewer than 4
minutes of headcam footage, 5 for having multiple adults present, 5 for
missing Communicative Development Inventory (CDI) data, 2 for missing
scene camera footage, 1 for fussiness, and one for sample symmetry. All
inclusion decisions were made independent of the results of subsequent
analyses. These data were also analyzed in Frank, Simmons, Yurovsky, and
Pusiol (2013) and Sanchez, Long, Kraus, and Frank (2018).

@@

The first face detection system made use of a series of Haar
feature-based cascade classifiers (Viola \& Jones, 2004) applied to each
individual frame. The second algorithm (based on work by K. Zhang et al.
(2016)) uses multi-task cascaded convolutional neural networks (MTCNNs)
for joint face detection and alignment, built to perform well in
real-world environments where varying illuminations and occlusions are
present. We used a Tensorflow implementation of this algorithm available
at \url{https://github.com/davidsandberg/facenet}.

@@

For face detection, MTCNN outperformed OpenPose when taking into account
only the composite F-score (0.89 MTCNN vs.~0.83 OpenPose). MTCNN and
OpenPose performed comparably with the random sample, with MTCNN having
higher precision on the high density sample, suggesting that OpenPose
generated slightly more false positives than MTCNN. ViolaJones performed
quite poorly relative to the other detectors, especially with respect to
the random sample. For wrist detection, OpenPose performed moderately
well (F = 0.74) with relatively high precision but low recall on the
randomly sampled frames (see Table 1). We thus analyze wrist detections,
with the caveat that we are likely underestimating the proportion of
hands in the dataset.

\begin{table}[ht]
\centering
\begin{tabular}{rllrrr}
\hline
Algorithm & Sample\ Type & P & R & F \\ 
\hline
MTCNN-Faces & High density & 0.89 & 0.92 & 0.90 \\ 
MTCNN-Faces & Random & 0.94 & 0.62 & 0.75 \\ 
OpenPose-Faces & High density & 0.78 & 0.93 & 0.84 \\ 
OpenPose-Faces & Random & 0.72 & 0.80 & 0.76 \\ 
ViolaJones-Faces & High density & 0.96 & 0.44 & 0.60 \\ 
ViolaJones-Faces & Random & 0.44 & 0.38 & 0.41 \\ 
OpenPose-Wrists & High density & 0.66 & 1.00 & 0.79 \\ 
OpenPose-Wrists & Random & 0.88 & 0.29 & 0.44 \\ 
\hline
\end{tabular}
\caption{Detector performance on both high density samples (where proportion of targets detected was high) and random samples (where frames were randomly selected). P, R, and F denote precision, recall, and F-score, respectively.} 
\vspace{-1em}
\end{table}

@@

First, we report developmental shifts in infants' posture and their
orientation relative to their caregiver, consistent with previous
literature (Adolph \& Berger, 2006; Franchak et al., 2017). Then, we
examine how these changes influence children's visual access to faces
and wrists/hands across this developmental time range, examining the
relative contributions of age vs.~postural developments. We also explore
how these changes impact the accessibility of faces and wrists/hands
during labeling events, both when parents were labeling familiar objects
(e.g., \enquote{cat}) as well as novel objects (e.g., \enquote{zem}).
Finally, we apply the same automated detection method to a egocentric
video dataset collected by a different lab (Franchak et al., 2017)
during which children's in-the-moment posture was annotated.

\begin{figure*}[!h]

{\centering \includegraphics[width=\textwidth]{figs/posture-1}

@@

\begin{figure*}[!h]

{\centering \includegraphics[width=\textwidth]{figs/indivPosOrient-1}

@@

We first examined the proportion of face and hand detections as a
function of children's age without considering their posture (see Figure
\ref{fig:detByAge}); here, we report face and wrist detections using
OpenPose, although the same pattern of results for face detections was
found using the outputs from MTCNN. While faces tended to be in the
field-of-view overall more often than hands, children's head-mounted
cameras were angled slightly upward to capture the presence of faces,
and hand detections suffered from somewhat lower recall than face
detections. Going forward, we thus analyze differences in the relative
proportion of faces or hands in view as a function of age, posture, and
orientation, rather than comparing them directly. Overall, we observed
that 12-month-olds appeared to have visual access to slightly fewer
faces than 8 or 16-month-olds, creating a slight U-shaped function in
face detections; conversely, hand detections were showed a slight
increase across this age range, as reported in prior literature (Fausey
et al., 2016).

However, these age-related trends were much smaller than the effect of
infant's postural developments on children's visual access to faces and
hands. Children's in-the-moment posture was a major factor both in how
many faces and hands were in view during the play session, as was their
orientation relative to their caregiver. Infants who were sitting or
standing had more faces in view than infants who were lying
down/crawling (i.e.~prone), which was most frequent among 12-month-olds
relative to the other age groups (Figure \ref{fig:detByPosOrient}). When
caregivers were behind their children, supporting their children's
sitting or standing positions, children saw fewer faces and wrists. In
particular, children who were sitting or in front of their caregiver had
a high proportion of faces and hands in their field of view (Figure
\ref{fig:detByPosOrient}).

@@

Our play session was designed to provide parents with opporunities to
label objects--both familiar and novel--such that we could examine
whether children sought out different kinds of social information around
naming events. We thus explored how face and hand detections changed
during object labeling events, analyzing a four-second window around
each labeling event (e.g., \enquote{Look at the {[}zem{]}!}). Every
utterance of one of the labelled objects (e.g., \enquote{ball}) was
counted as a \enquote{labeling event}; timestamps of the beginning of
each word were hand-annotated from transcripts ad synchronized with the
frame-by-frame detections. Overall, we did not find major differences in
face/hand detections during naming events relative to baseline, either
for novel objects or for familiar objects (see Figure
\ref{fig:detByNaming}). This was true both when we analyzed naming rates
with or without taking into account children's posture and orientation
relative to their caregiver. These results suggest that either children
did not actively seek out social information during this particular play
session around naming events, perhaps because were a limited number of
possible referents at any given time.

\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\
  \hline
Intercept & -3.35 & 0.17 & -19.49 & 0.000 \\
  Sit & 0.31 & 0.20 & 1.58 & 0.114 \\
  Stand & -0.02 & 0.20 & -0.12 & 0.905 \\
  Close & 0.03 & 0.19 & 0.15 & 0.882 \\
  Far & 0.46 & 0.24 & 1.93 & 0.053 \\
  Age (Scaled) & 0.14 & 0.11 & 1.22 & 0.223 \\
  Sit*Close & 0.92 & 0.07 & 13.31 & 0.000 \\
  Stand*Close & 1.30 & 0.08 & 16.02 & 0.000 \\
  Sit*Far & 0.54 & 0.07 & 7.37 & 0.000 \\
  Stand*Far & 1.24 & 0.09 & 14.18 & 0.000 \\
   \hline
\end{tabular}
\caption{Model coefficients from a generalized linear mixed models predicting the proportion of faces seen by infants (as detected by OpenPose).}
\end{table}

\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\
  \hline
Intercept & -4.28 & 0.23 & -18.67 & 0.000 \\
  Sit & 0.54 & 0.19 & 2.90 & 0.004 \\
  Stand & 0.61 & 0.23 & 2.63 & 0.009 \\
  Close & 0.67 & 0.22 & 3.05 & 0.002 \\
  Far & 0.33 & 0.24 & 1.35 & 0.176 \\
  Age (Scaled) & 0.45 & 0.13 & 3.35 & 0.001 \\
  Sit*Close & 0.34 & 0.09 & 3.93 & 0.000 \\
  Stand*Close & 0.73 & 0.09 & 7.92 & 0.000 \\
  Sit*Far & -0.15 & 0.11 & -1.39 & 0.165 \\
  Stand*Far & 1.32 & 0.11 & 11.70 & 0.000 \\
   \hline
\end{tabular}
\caption{Model coefficients from a generalized linear mixed models predicting the proportion of wrists seen by infants (as detected by OpenPose).}
\end{table}

\begin{figure*}[!h]

{\centering \includegraphics[width=\textwidth]{figs/detByAge-1}

@@

\begin{figure*}[!h]

{\centering \includegraphics[width=\textwidth]{figs/detByPosOrient-1}

@@

\begin{figure*}[!h]

{\centering \includegraphics[width=\textwidth]{figs/detByNaming-1}

@@

\subsection{Extension to Franchak et al.,
2017}\label{extension-to-franchak-et-al.-2017}

In the present work, we found that infant's in-the-moment posture
changed with their age, as did infants' orientation relative their
caregiver. In a related study with 12-month-olds, Franchak et al. (2017)
also that children's in-the-moment posture changed the amount of time
infants spent looking at faces. Here, we sought to replicate the
findings from Franchak et al. (2017) using our automated methodology
(OpenPose detections), using the footage from their head-mounted cameras
(D. A. Simon, Gordon, Steiger, \& Gilmore, 2015).

This dataset differed from the present in two key ways that could
present a challenge for our automated methodology. First, the
environment that infants were immersed in with their caregivers (and
experimenters) was much larger and more varied than the play room used
in the present dataset, containing multiple structures and toys in
different parts of the room for infants to explore, unlike the room used
for the present dataset which was relatively small (approximately 10' x
10'). Thus, our automated methodology could fail to generalize to scenes
from these more complex environments, where detecting faces and hands
could arguably be a much harder task. Second, Franchak et al. (2017)
used a head-mounted eye-tracker, finding that children's posture
affected where children were looking within their visual field.
Nonetheless, if children are often orienting their heads towards where
they are allocating their attention (Yoshida \& Smith, 2008) then we
should expect to find the same pattern of results only when analyzing
the information in view.

\begin{figure*}[!h]

{\centering \includegraphics[width=\textwidth]{figs/franchak-1}
